The Pair Distribution Function of the Inhomogeneous Hard-Sphere Fluid

### 2014-03-10 papers/pair-correlation/paper.tex
Made path plots nicer in pair-correlation paper. More changes to come. Tested on paho-arch. Took 1:17.44.

%\newcommand{\derivation}[1]{#1} % Use this to show all derivations in detail
\newcommand{\derivation}[1]{} % Use this for nice pegagogical paper...
\newcommand{\davidsays}[1]{{\color{red} [\green{David:} \emph{#1}]}}
\newcommand{\jeffsays}[1]{{\color{red} [\green{Jeff:} \emph{#1}]}}

@@

\newcommand\paircaption{\fixme{Look into smoothing the top plot on
    right.} The pair distribution function near a hard wall, with
  packing fractions of 0.1 and 0.3 and $\rr_1$ in contact with the
  hard wall.  On the left is a 2D plot of $g^{(2)}(\rr_1,\rr_2)$ as
  $\rr_2$ varies.  The top half of this figure shows the result of the
  Monte Carlo simulation, while the bottom half shows the result of
  the appproximation developed in this work.  On the right is a plot
  of $g^{(2)}(\rr_1,\rr_2)$ on the path illustrated in the figure to
  the left.  This plot compares the Monte Carlo results (black) with
  those of this work (blue), Sokolowski and Fischer
  (red)~\cite{sokolowski1992role}, and Fischer and Methfessel
  (green)~\cite{fischer1980born}.  The latter is only plotted at
  contact, where it is defined.  }

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-contact-3.pdf}\\
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-inbetween-3.pdf}
  \caption{\fixme{Remove one of, or make a note of, the two curves for
      this work}\fixme{Fix MC issue here (volume wrong?)} The triplet
    distribution function $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at packing
    fraction 0.3, plotted when $\rr_1$ and $\rr_2$ are in contact.
    The color plot on the left shows the triplet distribution
    function, with white corresponding to the contact value of the
    \emph{pair} distribution function.  The plot on the right shows
    the value of $g^{(3)}$ along the path shown as a dotted line on
    the plot to the left.}\label{fig:triplet-contact-distribution}
\end{figure*}

>>>>

%\newcommand{\derivation}[1]{#1} % Use this to show all derivations in detail
\newcommand{\derivation}[1]{} % Use this for nice pegagogical paper...
\newcommand{\davidsays}[1]{{\color{red} [\green{David:} \emph{#1}]}}
\newcommand{\jeffsays}[1]{{\color{red} [\green{Jeff:} \emph{#1}]}}
\newcommand{\pahosays}[1]{{\color{red} [\green{Paho:} \emph{#1}]}}

@@

\newcommand\paircaption{\pahosays{The MC has one point that jumps up at the
    beginning of the incontact region.} The pair distribution function near a
  hard wall, with packing fractions of 0.1 and 0.3 and $\rr_1$ in contact with
  the hard wall.  On the left is a 2D plot of $g^{(2)}(\rr_1,\rr_2)$ as $\rr_2$
  varies.  The top half of this figure shows the result of the Monte Carlo
  simulation, while the bottom half shows the result of the appproximation
  developed in this work.  On the right is a plot of $g^{(2)}(\rr_1,\rr_2)$ on
  the path illustrated in the figure to the left.  This plot compares the Monte
  Carlo results (black) with those of this work (blue), Sokolowski and Fischer
  (red)~\cite{sokolowski1992role}, and Fischer and Methfessel
  (green)~\cite{fischer1980born}.  The latter is only plotted at contact, where
  it is defined.  }

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-contact-3.pdf}\\
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-inbetween-3.pdf}
  \caption{\fixme{Remove one of, or make a note of, the two curves for this
      work}\fixme{Fix MC issue here (volume wrong?)} \fixme{Add backward curve
      for this work mc?}\fixme{z-axis wrong}The triplet
    distribution function $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at packing fraction 0.3,
    plotted when $\rr_1$ and $\rr_2$ are in contact.  The color plot on the left
    shows the triplet distribution function, with white corresponding to the
    contact value of the \emph{pair} distribution function.  The plot on the
    right shows the value of $g^{(3)}$ along the path shown as a dotted line on
    the plot to the left.}\label{fig:triplet-contact-distribution}
\end{figure*}
